\center \fontsize{18.8}{20} \selectfont Towards Globally Color-Dual Multi-Loop Integrands

### 2023-09-21 notes/2loopNLSM.tex

The kinematic numerators must be $D$-dimensional, Lorentz invariant,
local (polynomial) functions of the graph kinematics with the correct
power counting and external states. Locality is also physically motivated since Feynman
rules by construction produce polynomial numerators. Indeed, the most natural way to guarantee locality and avoid spurious poles is to require the off-shell numerators to be polynomial functions of
kinematics. However, insisting on a local numerator is
partly a matter of convenience as the ansatz for a rational function
would quickly grow out of control without a guiding principle for what
terms to include.  While these
assumptions are well motivated from a physical and complexity
standpoint, the literature has featured numerators that violate
locality, modify naive power counting through the inclusion of higher
spin modes, and break manifest Lorentz invariance \cite{Square,
  WeinzierlBCJLagrangian, Mogull:2015adi, FivePointN4BCJ,
  Johansson:2017bfl, Ben-Shahar:2022ixa, Cheung:2016prv,
  Cheung:2021zvb}.  These developments suggest that relaxing locality
is a viable alternative when the condition proves too stringent for an
ansatz. As such, requiring instead that locality is only realized \textit{on-shell} may suffice.
This alternative will be discussed in \cref{nonLocalScattering}.

@@

@@

In color-charged theories, both sides of the cut can be further
decomposed according to the color algebra.  For theories charged under
the adjoint of $SU(N)$ via $f^{abc}$-dressed amplitudes, it is
convenient to project onto a specific element of the Del
Duca-Dixon-Maltoni (DDM) color basis \cite{DixonMaltoni} by only
inserting color-ordered amplitudes, a la the right hand side of
\cref{eq:ddm-basis} in the product of trees, and restricting the set
of compatible diagrams to those whose color factors reduce to the
appropriate DDM element when summing over \emph{only the uncut color
  contractions}.  In this situation, the color becomes an overall
factor on the entire cut equality and thus can be ignored.  Cuts that
are organized in this manner are known as ``color-ordered'' cuts, in
the same sense as color-ordered tree amplitudes.  Since the DDM basis
(and dual Kleiss-Kuijf amplitude basis \cite{Kleiss:1988ne}) have
$(n-2)!$ elements, one generally needs to evaluate
$(n_1-2)! (n_2-2)!...$ separate color-orderings of the same cut, where
$n_1$, $n_2$... are the multiplicities of the amplitudes making up the
cut. As an example, consider the ``bowtie'' cut topology -- one of the
factorization channels of the iterated unitarity cut -- that has two
topologically distinct color-ordered expansions
\begin{equation}
  \label{eq:kt-color-ord}
   \NMCutC =
  \begin{cases}
     s\text{-}t \text{ channel}
    &
      \frac{1}{\textcolor{ucp-color}{s_{12}}}
      N \left[\scalebox{0.65}{\KTBTContrib{1}{4}{3}{2}}
      \right]
      +
      \frac{1}{\textcolor{ucp-color}{\ell_1^2}} \
      N \left[
      \scalebox{0.65}{\KTDBContrib{1}{4}{3}{2}}
      \right]\\
    t\text{-}u \text{ channel}
    & 
      \frac{1}{\textcolor{ucp-color}{\ell_1^2}} \
      N \left[
      \scalebox{0.65}{\KTDBContrib{1}{4}{3}{2}}
      \right]
      +
      \frac{1}{\textcolor{ucp-color}{\ell_2^2}} \
      N\left[
      \scalebox{0.65}{\KTDBContrib{1}{3}{4}{2}}
      \right]
  \end{cases}
\end{equation}
which serve as a complete basis for the full cut.

@@

At this point color-kinematics duality has been satisfied, so the
double copy will proceed without issue.  However, the plethora of
generalized gauge freedom parameters leaves the option for enforcing
additional aesthetic constraints.  All remaining generalized gauge
parameters could be set to zero, but a simpler and more insightful
result can be obtained through physical arguments.  $\mathcal{N}=4$
SYM provides several hints for further conditions to impose on the
ansatz.  For example, for maximally supersymmetric gauge theory it is
possible to enforce the no triangle hypothesis, manifest loop power
counting, and, for four-point and up to at least six loops, strip off
a factor of $st \atree$ from the integrand \cite{FiveLoopN4,
  Bern:2012uf, Bern:2010fy, SuperSum, Carrasco:2021otn,
  JJHenrikReview, BRY, BDDPR, Neq44np}.  For the NLSM integrand it is
desirable to make color-kinematics duality as manifest as possible.
One hope would be to factor out some piece of the one-loop numerator
since this at least manifests antisymmetry for the vertices involving
external legs.  However, a more fruitful direction is to match onto
the one known theory with pion power counting that manifests
color-kinematics duality to all loop orders, namely,
Zakharov-Mikhailov (ZM) theory \cite{Zakharov:1973pp,
  Cheung:2022mix}. ZM theory is governed by the Lagrangian
\begin{equation}
\label{eq:ZMLagrangian}
\mathcal{L}^{\text{ZM}} = \frac{1}{2}(\partial \varphi)^2
+ g f^{abc} \varphi^a \varepsilon^{\mu\nu}(\partial_\mu \varphi^b)( \partial_\nu \varphi^c),
\end{equation}
where more details can be found in \cref{sec:CKLagrangians}.  The
color-stripped Feynman rule for the vertex is
$V(k_1, k_2, k_3) \propto \varepsilon_{\mu\nu}k_1^\mu k_2^\nu$ where
off-shell color-kinematics duality to all orders in perturbation
theory simply follows from the Schouten identity in 2D.  Since the theory
only has a cubic vertex and manifest off-shell color-kinematics
duality, it is trivial to read off the color-dual numerator for any
graph.  From the presence of the Levi-Civita tensor
$\varepsilon^{\mu\nu}$, the theory clearly resides in two spacetime
dimensions where scattering is notoriously plagued by infrared
regulation issues.  Every on-shell particle is either a right mover,
with momentum proportional to $k_R^\mu \equiv (1,1)$, or a left mover,
with momentum proportional to $k_L^\mu \equiv (1,-1)$.  On-shell ZM
amplitudes naturally divide into sectors corresponding to the
configuration of left and right movers, where the scattering in many
sectors is rather subtle.  Only color-ordered amplitudes can be
defined unambiguously from the Feynman rules.  At four-point, only the
alternating sector is free of subtleties and the amplitude for this
process vanishes.  In equations, $A[LRLR]=0$ where $R$ corresponds to
a right mover and $L$ corresponds to a left mover.  In every other
configuration of right and left movers, such as $A[RRRR]$, one of the
internal propagators is accidentally on-shell since $k_R^2=k_L^2=0$.

\ace{Lets tighten up this paragraph a bit, especially the second half}
It is tempting to try to match the pion four-point two-loop integrand
to ZM on the cuts, but given that the cuts only probe the on-shell
four-point amplitude, which is either subtle or vanishes for ZM, it is
better to compare the off-shell numerators directly.  As local
functions, the numerators never suffer from any of the subtleties of
on-shell 2D kinematics.  Since the physical cuts are difficult to
compare, ZM theory is being used here simply as a tool to eliminate
generalized gauge freedom; ZM theory has the right power counting and
kinematic structure in 2D to compare against.  Since ZM theory is only
being used for the kinematical structure of its numerators, it is
natural to introduce a proportionality constant $z$ between the NLSM
and ZM numerators $n_\text{NLSM} \vert_{2D} = z ~ n_\text{ZM}$.  The
parameter $z$, which would normally be fixed on cuts, effectively
encodes the discrepancy between the coupling constants of the two
theories.\footnote{Floating the proportionality parameter $z$ is also
  motivated because ZM is believed to be quantum mechanically
  different from NLSM even though they are dual classically in two
  dimensions \cite{Nappi:1979ig}.  When the four-point
  pion amplitude is normalized to $-k_1\cdot k_2$ and the ZM vertex is
  normalized to $k_1^\mu \varepsilon_{\mu\nu}k_2^\nu$, the parameter
  $z$ is fixed to $216/565$, which is clearly unrelated to the
  difference in coupling constants.}  This introduces an extra degree of
freedom into the problem.  Mechanically, the pion numerator is matched
to ZM by first taking every possible assignment of right and left
movers for the external particles and then restricting the pion
numerator to 2D.  The loop momenta are restricted to 2D but left
off-shell.  After performing the 2D matching to the following ZM basis numerators:
\be
\ZMBasisDoubleBox =\left[\begin{split}
  \langle (l_1+k_4) l_1 \rangle\langle l_1l_2 \rangle\langle l_2 (l_2+k_1) \rangle  \langle (l_2+k_1)(l_2+k_1+k_2) \rangle 
\\
\langle (l_1+k_3+k_4)(l_2+k_1+k_2) \rangle\langle (l_1+k_3+k_4)(l_1+k_4) \rangle
\end{split}\right]
\ee
\be
\ZMBasisPentaTriangle =\left[\begin{split}
  \langle (l_1+k_4) l_1 \rangle\langle l_1l_2 \rangle\langle l_2 (l_2+k_1) \rangle  \langle (l_2+k_1)(l_1-k_1) \rangle 
\\
\langle (l_1+k_3+k_4)(l_1-k_1) \rangle\langle (l_1+k_3+k_4)(l_1+k_4) \rangle
\end{split}\right]
\ee
there are only 365 parameters of generalized gauge freedom. An overview of ZM theory and its color-dual construction can be found at the end of \cref{sec:CKLagrangians}. The loop momentum structure of ZM theory provides one final hint for
simplifying the pion numerators.  A generic term in the ZM numerator
(of either basis graph) looks schematically like
\begin{equation}
\label{eq:ZMLoopPowCount}
\ell_1^m \ell_2^n k^{12-(m+n)} \text{ where } 5 \leq m+n \leq 8,
\end{equation}
whereas a generic set of local, cubic Feynman rules could have
produced terms with up to $m+n=12$ powers of loop momenta.  When the
pion numerator is forced to have the loop power counting structure in
\cref{eq:ZMLoopPowCount} of ZM theory, the number of generalized gauge
freedom parameters reduces to 58.  The pion numerator appearing in the
ancillary files makes exactly this choice.

@@

The color-stripped Feynman rule for the three-point vertex can be read
off from the Lagrangian \cref{eq:ZMLagrangian}, giving
\begin{equation}
\langle ab\rangle \equiv p_a^\mu \varepsilon_{\mu\nu} p_b^\nu =p_a^0 p_b^1 - p_a^1 p_b^0 = -\langle ba \rangle .
\end{equation}
Unlike $J$-theory and $YZ$-theory, the vertex is (1) functionally symmetric and (2) the kinematic portion
of the vertex is completely anti-symmetric:
\begin{equation}
\cubic{hgrey0}{}{nhpBlue}{}{nhpBlue}{}{nhpBlue} = \langle 12\rangle = \langle 23\rangle = \langle 31\rangle = -\langle 21\rangle
\end{equation}
This important property is due to momentum conservation alone and does
not need any additional kinematic constraints to satisfy the duality.
To prove off-shell color kinematics duality for any multiplicity and
loop order it is enough to observe that the sum of the off-shell $s$-,
$t$-, and $u$-channel numerators sum to zero
\begin{equation}
\label{eq:ZMJacobi}
\langle ab \rangle \langle cd\rangle +\langle ac \rangle \langle db\rangle +\langle ad \rangle \langle bc\rangle =0 % \delta^{[a}_c\delta^{b]}_d + \delta^{[a}_d\delta^{c]}_b+ \delta^{[a}_b\delta^{d]}_c
\end{equation}
by virtue of the 2D Levi-Civita identity
$\varepsilon_{\mu\nu}\varepsilon_{\rho\sigma} =
\eta_{\mu\rho}\eta_{\nu\sigma}-\eta_{\mu\sigma}\eta_{\nu\rho}$.
Amusingly, \cref{eq:ZMJacobi} is simply a manifestation of the
Schouten identity. Below we provide the double-box and penta-triangle expressions to which we matched our NLSM integrands to in the text:
\begin{equation}
\ZMBasisDoubleBox =\left[\begin{split}
  \langle (\ell_1+k_4) \ell_1 \rangle\langle \ell_1\ell_2 \rangle\langle \ell_2 (\ell_2+k_1) \rangle  \langle (\ell_2+k_1)(\ell_2+k_1+k_2) \rangle 
\\
\langle (\ell_1+k_3+k_4)(\ell_2+k_1+k_2) \rangle\langle (\ell_1+k_3+k_4)(\ell_1+k_4) \rangle
\end{split}\right]
\end{equation}
\begin{equation}
  \ZMBasisPentaTriangle =\left[
    \begin{split}
      \langle (\ell_1+k_4) \ell_1 \rangle\langle \ell_1\ell_2 \rangle\langle \ell_2 (\ell_2+k_1) \rangle  \langle (\ell_2+k_1)(\ell_1-k_1) \rangle 
      \\
      \langle (\ell_1+k_3+k_4)(\ell_1-k_1) \rangle\langle (\ell_1+k_3+k_4)(\ell_1+k_4) \rangle
    \end{split}
  \right]
\end{equation}
Furthermore, since ZM theory manifests color-kinematics duality
without any reference to the on-shell condition, a mass term can be
added to ZM theory without spoiling color-kinematics duality
\cite{Cheung:2022mix}. In general, if the on-shell conditions are not
used, color-kinematics duality is unaffected by the details of the
propagator structure.

>>>>

The kinematic numerators must be $D$-dimensional, Lorentz invariant,
local (polynomial) functions of the graph kinematics with the correct
power counting and external states. Locality is also physically motivated since Feynman
rules by construction produce polynomial numerators. Indeed, the most natural way to guarantee locality and avoid spurious poles is to require the off-shell numerators to be polynomial functions of
kinematics. However, insisting on a local numerator is
partly a matter of convenience as the ansatz for a rational function
would quickly grow out of control without a guiding principle for what
terms to include.  While these
assumptions are well motivated from a physical and complexity
standpoint, the literature has featured numerators that violate
locality, modify naive power counting through the inclusion of higher
spin modes, and break manifest Lorentz invariance \cite{Square,
  WeinzierlBCJLagrangian, Mogull:2015adi, FivePointN4BCJ,
  Johansson:2017bfl, Ben-Shahar:2022ixa, Cheung:2016prv,
  Cheung:2021zvb}.  These developments suggest that relaxing locality
is a viable alternative when the condition proves too stringent for an
ansatz.  In particular, the most natural way to guarantee locality is
to require the off-shell numerators to be polynomial functions of
kinematics.  However, simply requiring on-shell locality may suffice.
This alternative will be discussed in \cref{nonLocalScattering}.

@@

\begin{figure}
\centering
{\MCutC, \MCutD, \sumoCut, \MCutJ,  
 \\
  \doubleBoxCut,  \crossBoxCut,\pentaTriangleCut,  \MCutF, 
\\
\MCutI,  \MCutE, \MCutK, 
\\
 \MCutL, \MCutG,  \MCutH
}
\caption{The 14 non-pathological four-point two-loop cubic diagrams.} \label{fig:MaxCuts}
  \end{figure}

@@

In color-charged theories, both sides of the cut can be further
decomposed according to the color algebra.  For theories charged under
the adjoint of $SU(N)$ via $f^{abc}$-dressed amplitudes, it is
convenient to project onto a specific element of the Del
Duca-Dixon-Maltoni (DDM) color basis \cite{DixonMaltoni} by only
inserting color-ordered amplitudes, a la the right hand side of
\cref{eq:ddm-basis} in the product of trees, and restricting the set
of compatible diagrams to those whose color factors reduce to the
appropriate DDM element when summing over \emph{only the uncut color
  contractions}.  In this situation, the color becomes an overall
factor on the entire cut equality and thus can be ignored.  Cuts that
are organized in this manner are known as ``color-ordered'' cuts, in
the same sense as color-ordered tree amplitudes.  Since the DDM basis
(and dual Kleiss-Kuijf amplitude basis \cite{Kleiss:1988ne}) have
$(n-2)!$ elements, one generally needs to evaluate
$(n_1-2)! (n_2-2)!...$ separate color-orderings of the same cut, where
$n_1$, $n_2$... are the multiplicities of the amplitudes making up the
cut. As an example, consider the ``bowtie'' cut topology -- one of the
factorization channels of the iterated unitarity cut -- that has two
topologically distinct color-ordered expansions
\begin{equation}
  \label{eq:kt-color-ord}
\!\!\! \!\!\! \!  \NMCutC =
  \begin{cases}
     s\text{-}t \text{ channel}
    &
      \frac{1}{\textcolor{ucp-color}{s_{12}}}
      N \left[\scalebox{0.65}{\KTBTContrib{1}{4}{3}{2}}
      \right]
      +
      \frac{1}{\textcolor{ucp-color}{\ell_1^2}} \
      N \left[
      \scalebox{0.65}{\KTDBContrib{1}{4}{3}{2}}
      \right]\\
    t\text{-}u \text{ channel}
    & 
      \frac{1}{\textcolor{ucp-color}{\ell_1^2}} \
      N \left[
      \scalebox{0.65}{\KTDBContrib{1}{4}{3}{2}}
      \right]
      +
      \frac{1}{\textcolor{ucp-color}{\ell_2^2}} \
      N\left[
      \scalebox{0.65}{\KTDBContrib{1}{3}{4}{2}}
      \right]
  \end{cases}
\end{equation}
which serve as a complete basis for the full cut.

@@

At this point color-kinematics duality has been satisfied, so the
double copy will proceed without issue.  However, the plethora of
generalized gauge freedom parameters leaves the option for enforcing
additional aesthetic constraints.  All remaining generalized gauge
parameters could be set to zero, but a simpler and more insightful
result can be obtained through physical arguments.  $\mathcal{N}=4$
SYM provides several hints for further conditions to impose on the
ansatz.  For example, for maximally supersymmetric gauge theory it is
possible to enforce the no triangle hypothesis, manifest loop power
counting, and, for four-point and up to at least six loops, strip off
a factor of $st \atree$ from the integrand \cite{FiveLoopN4,
  Bern:2012uf, Bern:2010fy, SuperSum, Carrasco:2021otn,
  JJHenrikReview, BRY, BDDPR, Neq44np}.  For the NLSM integrand it is
desirable to make color-kinematics duality as manifest as possible.
One hope would be to factor out some piece of the one-loop numerator
since this at least manifests antisymmetry for the vertices involving
external legs.  However, a more fruitful direction is to match onto
the one known theory with pion power counting that manifests
color-kinematics duality to all loop orders, namely,
Zakharov-Mikhailov (ZM) theory \cite{Zakharov:1973pp, Cheung:2022mix}.
ZM theory is governed by the Lagrangian
\begin{equation}
\label{eq:ZMLagrangian}
\mathcal{L}^{\text{ZM}} = \frac{1}{2}(\partial \varphi)^2
+ g f^{abc} \varphi^a \varepsilon^{\mu\nu}(\partial_\mu \varphi^b)( \partial_\nu \varphi^c),
\end{equation}
where more details can be found in \cref{sec:CKLagrangians}.  The
color-stripped Feynman rule for the vertex is
$V(k_1, k_2, k_3) \propto \varepsilon_{\mu\nu}k_1^\mu k_2^\nu$ where
off-shell color-kinematics duality to all orders in perturbation
theory simply follows from the Schouten identity in 2D.  Since the theory
is purely cubic and manifests off-shell color-kinematics
duality, it is trivial to read off the color-dual numerator for any
graph.  From the presence of the Levi-Civita tensor
$\varepsilon^{\mu\nu}$, the theory clearly resides in two spacetime
dimensions where scattering is notoriously plagued by infrared
regulation issues.  Every on-shell particle is either a right mover,
with momentum proportional to $k_R^\mu \equiv (1,1)$, or a left mover,
with momentum proportional to $k_L^\mu \equiv (1,-1)$.  On-shell ZM
amplitudes naturally divide into sectors corresponding to the
configuration of left and right movers, where the scattering in many
sectors is rather subtle.  Only color-ordered amplitudes can be
defined unambiguously from the Feynman rules.  At four-point, only the
alternating sector is free of subtleties and the amplitude for this
process vanishes.  In equations, $A[LRLR]=0$ where $R$ corresponds to
a right mover and $L$ corresponds to a left mover.  In every other
configuration of right and left movers, such as $A[RRRR]$, one of the
internal propagators is accidentally on-shell since $k_R^2=k_L^2=0$.

It is tempting to try to match the pion four-point two-loop integrand to ZM
on the cuts, but given that the cuts only probe the on-shell four-point
amplitude, which is either subtle or vanishes for ZM, it is better to
compare the off-shell numerators directly.
The numerators of the two basis graphs are
\be
\ZMBasisDoubleBox =\left[\begin{split}
  \langle (l_1+k_4) l_1 \rangle\langle l_1l_2 \rangle\langle l_2 (l_2+k_1) \rangle  \langle (l_2+k_1)(l_2+k_1+k_2) \rangle 
\\
\langle (l_1+k_3+k_4)(l_2+k_1+k_2) \rangle\langle (l_1+k_3+k_4)(l_1+k_4) \rangle
\end{split}\right]
\ee
\be
\ZMBasisPentaTriangle =\left[\begin{split}
  \langle (l_1+k_4) l_1 \rangle\langle l_1l_2 \rangle\langle l_2 (l_2+k_1) \rangle  \langle (l_2+k_1)(l_1-k_1) \rangle 
\\
\langle (l_1+k_3+k_4)(l_1-k_1) \rangle\langle (l_1+k_3+k_4)(l_1+k_4) \rangle
\end{split}\right]
\ee
where $\langle ab\rangle \equiv p_a^\mu \varepsilon_{\mu\nu} p_b^\nu$ is the color-stripped ZM vertex.
As local functions, the
numerators never suffer from any of the subtleties of on-shell 2D
kinematics.
We introduce a proportionality constant $z$ between the numerators of the two theories, $N_\text{NLSM} \vert_{2D} = z ~ N_\text{ZM}$, because we are only interested in how the kinematical structure of $N_\text{ZM}$ can be used to eliminate gauge freedom in $N_\text{NSLM}$.\footnote{Another reason for introducing the parameter $z$ is because the theories are believed to differ at loop level even though they are dual classically in 2D \cite{Nappi:1979ig}.  Once all of the constraints from this section are imposed, $z$ is fixed to $216/565$ where the four-point pion tree amplitude is normalized to $-k_1\cdot k_2$ and the ZM vertex is normalized to $k_1^\mu \varepsilon_{\mu\nu}k_2^\nu$.}
Mechanically, the pion numerator is matched
to ZM by first taking every possible assignment of right and left
movers for the external particles and then restricting the pion
numerator to 2D.  The loop momenta are restricted to 2D but left
off-shell.  After performing the 2D matching, there are only 365
parameters of generalized gauge freedom.

The loop momentum structure of ZM theory provides one final hint for
simplifying the pion numerators.  A generic term in the ZM numerator
(of either basis graph) looks schematically like
\begin{equation}
\label{eq:ZMLoopPowCount}
\ell_1^m \ell_2^n k^{12-(m+n)} \text{ where } 5 \leq m+n \leq 8,
\end{equation}
whereas a generic set of local, cubic Feynman rules could have
produced terms with up to $m+n=12$ powers of loop momenta.  When the
pion numerators are forced to have the loop power counting structure in
\cref{eq:ZMLoopPowCount} of ZM theory, the number of generalized gauge
freedom parameters reduces to 58.  The pion numerators appearing in the
ancillary files make exactly this choice.

@@

The color-stripped Feynman rule for the three-point vertex can be read
off from the Lagrangian \cref{eq:ZMLagrangian}, giving
\begin{equation}
\langle ab\rangle \equiv p_a^\mu \varepsilon_{\mu\nu} p_b^\nu =p_a^0 p_b^1 - p_a^1 p_b^0 = -\langle ba \rangle .
\end{equation}
Unlike $J$-theory and $YZ$-theory, the vertex is (1) functionally symmetric and (2) the kinematic portion
of the vertex is completely anti-symmetric:
\begin{equation}
\cubic{hgrey0}{}{nhpBlue}{}{nhpBlue}{}{nhpBlue} = \langle 12\rangle = \langle 23\rangle = \langle 31\rangle = -\langle 21\rangle
\end{equation}
This important property is due to momentum conservation alone and does
not need any additional kinematic constraints to satisfy the duality.
To prove off-shell color kinematics duality for any multiplicity and
loop order it is enough to observe that the sum of the off-shell $s$-,
$t$-, and $u$-channel numerators sum to zero
\begin{equation}
\label{eq:ZMJacobi}
\langle ab \rangle \langle cd\rangle +\langle ac \rangle \langle db\rangle +\langle ad \rangle \langle bc\rangle =0 % \delta^{[a}_c\delta^{b]}_d + \delta^{[a}_d\delta^{c]}_b+ \delta^{[a}_b\delta^{d]}_c
\end{equation}
by virtue of the 2D Levi-Civita identity
$\varepsilon_{\mu\nu}\varepsilon_{\rho\sigma} =
\eta_{\mu\rho}\eta_{\nu\sigma}-\eta_{\mu\sigma}\eta_{\nu\rho}$.
Amusingly, \cref{eq:ZMJacobi} is simply a manifestation of the
Schouten identity.
Since ZM theory manifests color-kinematics duality without any
reference to the on-shell condition, a mass term can be added to ZM
theory without spoiling color-kinematics duality \cite{Cheung:2022mix}. In general, if the
on-shell conditions are not used, color-kinematics duality is
unaffected by the details of the propagator structure.
